---
title: "The Data Science in Everyday Music Listening"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill

---

```{r setup, include=FALSE}
library(flexdashboard)
```

About {data-orientation=columns}
====================================================

Inputs {.sidebar}
-------------------------------------
links  referenced material?


```{r}
```

Column 
-------------------------------------

### Chart A1
why we chose this subject matter

```{r}

```

### Chart A2
our raw data in a table
```{r}

```


Column 
-------------------------------------

### Chart A3
what we aim to find

```{r}

```
 
Methodology {data-orientation=rows}
=============================================

Row {data-height=650}{.tabset}
-------------------------------------

### General information 
consent explained

```{r} 
```
### GOLD MSI
Musical sophistication check explained
```{r}
```
### 2 Variable Emotion
emotion check explained
```{r} 
```

### Attention
  attention check explained
```{r} 
```

Row {data-height=350}
-------------------------------------
   
### Expected Chart before

```{r}
library(ggplot2)
sample(1:70, 100, replace = T)-> valence
sample(1:70, 100, replace = T) -> energy
ggplot(data = NULL, aes(x = valence, y = energy)) +
  geom_point()
```   
    
### Expected Chart after

```{r}
library(ggplot2)
sample(1:70, 100, replace = T)-> valence
sample(1:70, 100, replace = T) -> energy
ggplot(data = NULL, aes(x = valence - 10, y = energy - 10)) +
  geom_point()
```



Results {data-orientation=rows}
=============================================

Row
-------------------------------------
    
### before
    
```{r}
library(ggplot2)
sample(1:70, 100, replace = T)-> valence
sample(1:70, 100, replace = T) -> energy
ggplot(data = NULL, aes(x = valence - 10, y = energy - 10)) +
  geom_point()
```
    
### after

```{r}
library(ggplot2)
sample(1:70, 100, replace = T)-> valence
sample(1:70, 100, replace = T) -> energy
ggplot(data = NULL, aes(x = valence - 10, y = energy - 10)) +
  geom_point()
```




Row
-------------------------------------
    
### age distribution
    
```{r}
```
 
### Country distribution
    
```{r}
slices <- c(10, 12, 4, 16, 8)

lbls <- c("US", "UK", "Australia", "Germany", "France")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct)
# add percents to labels
lbls <- paste(lbls,"%",sep="") # ad % to labels
pie(slices,labels = lbls, col=rainbow(length(lbls)),
   main="Pie Chart of Countries")
``` 

### sophistication to change in mood?
    
```{r}
  sophistication <- c(1,2,3,5,5,6,6,6,7,8,8,9,9,10,11,12,12,14,15,15,15,15,16,17,19,20,21,21,22,22,23,24,24,24,25,25,25,26,27,27,29,29,30,30,32,32,33,33,34,35,35,35,36,36,36,36,37,37,38,38,39,40,41,42,43,44,45,45,48,50,50,52,54,54,55,55,55,55,56,56,57,57,59,59,60,61,62,62,63,63,64,64,64,65,65,66,67,68,68,70)
  distance <- c(1,1,2,3,5,6,7,7,8,8,8,9,10,12,12,13,13,13,14,14,15,15,15,16,16,19,19,19,19,21,21,21,22,24,25,25,25,25,27,27,27,28,28,28,29,29,30,31,31,32,32,33,33,33,34,37,37,38,41,42,43,45,46,46,48,48,48,49,49,50,50,52,52,53,54,54,55,56,57,57,57,58,58,59,59,60,60,60,61,62,64,64,64,65,66,66,66,66,68,70)
  ggplot(data = NULL, aes(x = valence - sophistication, y = distance)) +
  geom_point()
``` 

